Insert the article title here

### 2020-07-22 tex/results.tex
Better captions for figure

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    short edge configuration (electric field parallel to the shorter dimension)}
    \label{fig:ext_y_14a}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    long edge configuration (electric field parallel to the longer dimension)}
    \label{fig:ext_y_14b}
 \end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
    \caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
            Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
            electric field parallel to the short dimension (b), and the geometry is in air. 
            Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
            short edge configuration (electric field parallel to the shorter dimension)}
    \label{fig:ext_y_14a}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
    \caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
    Attempt of replication of Figure 14b on Rockstuhl paper (case a1). In this case we have the constant 
    electric field parallel to the long dimension (a), and the geometry is in air.
        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    long edge configuration (electric field parallel to the longer dimension)}
    \label{fig:ext_y_14b}
 \end{figure}
